Well-quasi-orderings on word languages

### 2024-10-17 src/conclusion.tex
Add lex

>>>>

\subparagraph{Lexicographic orderings} There is another natural ordering on
words, the \emph{lexicographic ordering}, which does not fit well in our
current framework because it is always of \kl{ordinal width} $0$. However, the
\kl{order-type} of the lexicographic ordering over \kl{regular languages} has
already been investigated in the context of infinite words, and it would be
interesting to see if one can extend these results to decide whether such an
ordering is \kl{well-founded} for languages recognized by \kl{amalgamation
systems}.
